Missing data: Current practice in football research and recommendations for

### 2020-10-03 paper/paper.Rmd
edit wording in the conclusion.
update mismatch csv and main document edits

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@PRISMA]. Football related
articles published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 2). Included articles were: (a) written in English; (b) had an accessible
full-text; and (c) included quantitative data. The PRISMA figure in Supplement 2 summarises the search process,
and further details of the search can also be found in Supplement 2.

@@

Of the 199 articles screened, 136 met the inclcusion criteria, representing
\~10% of the articles found (see Supplement 2, Figure 1). The proportion of
articles that reported missing data was 5.9% (95% confidence interval;
X% to X%) or 8/136. Of the articles that did not mention missing data
(128/136), 7.1% (3.3% to 13.1%) or 9/128 shared their dataset, making
it difficult to determine whether there was any missingness. While the
absence of a missing data statement does not necessarily mean missing
data are not being reported, it does suggest that this aspect of the
analysis process receives little consideration--especially in contrast
to many of the papers that included (potentially meaningless) tests of
normality (e.g., Kruskall-Wallis test).

@@

Our survey of 2019 articles on football related topics
showed that current practice of reporting missing data is poor, 
with only about one in 20 studies reported missing data. 
This could suggest that this aspect of data anlaysis receives little attention. 
To address this issue and assist researchers,
we have provided recommendations for reporting and exploring missing data.
Research should consider these recommendations, and pay greater
attention to missing data and its influence on research results.

>>>>

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@PRISMA]. Articles on football topics (or involving footballers) published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 2). Included articles were: (a) written in English; (b) had an accessible
full-text; and (c) included quantitative data. The PRISMA figure in Supplement 2 summarises the search process,
and further details of the search can also be found in Supplement 2.

@@

Of the 199 articles screened, 136 met the inclusion criteria, representing
\~10% of the articles found (see Supplement 2, Figure 1). The proportion of
articles that reported missing data was 5.9% (95% confidence interval;
X% to X%) or 8/136. Of the articles that did not mention missing data
(128/136), 7.1% (3.3% to 13.1%) or 9/128 shared their dataset, making
it difficult to determine whether there was any missingness. While the
absence of a missing data statement does not necessarily mean missing
data are not being reported, it does suggest that this aspect of the
analysis process receives little consideration--especially in contrast
to many of the papers that included (potentially meaningless) tests of
normality (e.g., Kruskall-Wallis test).

@@

Our survey of 2019 articles on football related topics
showed that current practice of reporting missing data is poor, 
with only about one in 20 studies reported missing data. 
This could suggest that this aspect of data anlaysis receives little attention. 
To address this issue and assist researchers,
we have provided recommendations for reporting and exploring missing data.
Researchers should consider these recommendations, and pay greater
attention to missing data and its influence on research results.
